Approximation as Differentiation

### 2025-07-03 main/approx-as-tangents.tex
taylor99.

    In terms of \GPS the $\mathrm{gustave}$ function does not present a problem. For any particular run (i.e., input$\mapsto$output pair), there is an unambiguous minimal input that achieves the output, no matter that it was not achieved by a sequential processing of the input.

@@

The fact that these two functions's stability witnesses reveal information about how they depend on their input is what we will exploit in order to use the idea of stability for \GPS. It is interesting that sequentiality is not necessarily required in order to obtain backwards maps of approximations, as might be assumed by thinking about how to trace computations for provenance information.

Stability has an alternative definition in terms of Galois connections, which will be more useful for what follows. This characterisation is due to Paul Taylor\bob{cite}. We first formally define Galois connections, which we used informally in \exref{introduction-example}.

>>>>

    In terms of \GPS the $\mathrm{gustave}$ function does not present a problem. For any particular run (i.e., input $\mapsto$ output pair), there is an unambiguous minimal input that achieves the output, no matter that it was not achieved by a sequential processing of the input.

@@

The fact that these two functions' stability witnesses reveal information about how they depend on their input is what we will exploit in order to use the idea of stability for \GPS. It is interesting that sequentiality is not necessarily required in order to obtain backwards maps of approximations, as might be assumed by thinking about how to trace computations for provenance information.

Stability has an alternative definition in terms of Galois connections, which will be more useful for what follows. This characterisation is due to~\citet{taylor99}. We first formally define Galois connections, which we used informally in \exref{introduction-example}.
